\documentclass[10pt,a4paper]{article}

\usepackage{geometry}
\geometry{
  top    = 0.35in,
  bottom = 0.35in,
  left   = 0.30in,
  right  = 0.30in
}
\setlength\parindent{0pt}
\setlength\parskip{1.5pt}
\usepackage{multicol}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage[sc]{mathpazo}
\linespread{1.05}

\usepackage{enumitem}
\setlist[itemize]{leftmargin=*,nosep}

\usepackage{hyperref}
\usepackage{titlesec}

\titleformat{\section}
  {\large\bfseries}
  {}
  {0pt}
  {}
  [\vspace{-0.6em}\rule{\linewidth}{0.4pt}\vspace{-0.4em}]

\titleformat{\subsection}
  {\bfseries}
  {}
  {0pt}
  {}

\titlespacing*{\section}{0pt}{1ex}{0.7ex}
\titlespacing*{\subsection}{0pt}{0.5ex}{0.5ex}

\begin{document}

\begin{center}
  {\Huge\textbf{Léopold Chappuis}}\\[0.3em]
  Québec, Canada \;|\;
  \href{mailto:leopold@chappuis.fr}{leopold@chappuis.fr} \;|\;
  +33 6 24 88 42 96 \;|\;
  \href{https://github.com/leopoldch}{github.com/leopoldch}
\end{center}

\section*{Education}

\textbf{Université de Technologie de Compiègne}, 
\textit{Master of Science, Computer Science Engineering} 
\hfill 2021 – 2026 (expected)
GPA: 4/4
\par\vspace{0.1em} 
\textbf{Université Laval}, 
\textit{Master of Science, Computer Science Engineering} 
\hfill 2025 – 2027 (expected)
\par\vspace{0.4em} 
\textbf{Courses: }
Algorithms \& Data Structures,
Object-Oriented Design \& Programming,
Operating Systems (UNIX),
Computer Networks \& Security,
Machine Learning,
Artificial Intelligence,
Database Systems,
Distributed Systems,
Embedded Systems,
Probability \& Statistics,
Automatic \& Robotics
DevOps \& cloud-native applications,
Software Quality, 
Mobile networks

\par\vspace{0.4em} 
\section*{Experiences}

\textbf{Fit Coding Challenge}, Mostar, Bosnia and Herzegovina \hfill May 2025  
\begin{itemize}[leftmargin=*]
  \item Competitive programming \textbf{(C++)} event focused on solving advanced algorithmic problems, similar to LeetCode challenges, under time constraints.
\end{itemize}

\textbf{1st Prize — UTAC Autonomous Vehicle Competition}, \textit{Utonome} — Linas-Montlhéry proving ground, France \hfill May 2025  
\begin{itemize}[leftmargin=*]
  \item Developed ACC, obstacle avoidance, and decision algorithms for an autonomous vehicle.  
  \item Set up ROS-based real-time communication between server and vehicle.
\end{itemize}

\textbf{Free Software Engineer Intern}, \textit{Savoir-faire Linux} — Montréal, Canada \hfill Aug 2024 – Feb 2025
\begin{itemize}[leftmargin=*]
  \item Core contributor to Jami (peer-to-peer DHT, C++).
\end{itemize}

\textbf{Machine Learning Engineer}, \textit{Freelance} — Remote \hfill Feb 2024 - July 2025

\begin{itemize}
  \item Worked for the Urban Research Department at the technical University of Compiègne. Urban traffic forecasting — TensorFlow, LSTM, SARIMAX.
\end{itemize}

\textbf{Sysadmin}, \textit{Freelance} — Remote \hfill Oct 2023 – Aug 2024

\begin{itemize}
  \item Hosted, secured and maintained Drupal \& WordPress infrastructures, applying CI/CD and GDPR best practices.
\end{itemize}

\textbf{IT Service President}, \textit{Students’ Federation, UTC} — Compiègne, France \hfill May 2022 – May 2023

\begin{itemize}
  \item Managed an IT ecosystem for 150 associations (mail servers, web hosting, LDAP directory, monitoring).
\end{itemize}

\textbf{Event Technician}, \textit{Weezevent}  — France \hfill Jun 2022 – Present

\begin{itemize}
  \item Managed payment and access-control systems for large-scale festivals, ensuring real-time reliability.
\end{itemize}

\par\vspace{0.4em} 
\section*{Projects}

\textbf{AI – Board Game} \hfill 2024

\begin{itemize}
  \item Implemented Min-Max, Negamax, Alpha-Beta Pruning and Monte-Carlo Tree Search in Prolog to create a competitive AI.
\end{itemize}

\textbf{C Development (Algorithms \& Systems)} \hfill 2024

\begin{itemize}
  \item Built AVL trees, stacks, queues and IPC mechanisms (threads, semaphores, signals) to benchmark data-structure trade-offs.
\end{itemize}

\textbf{Board Game in C++17 \& Qt6} \hfill 2024

\begin{itemize}
  \item Designed an interactive board-game GUI, applying OOP and design-pattern best practices for maintainability.
\end{itemize}

\textbf{Breast-Cancer Prediction – Machine Learning} \hfill 2023

\begin{itemize}
  \item Compared classifiers (Correlation Matrix, Naïve Bayes, Random Forest, KNN, LDA/QDA, Logistic Regression) to maximise AUC.
\end{itemize}

\textbf{Inventory solution for an Association (React / Django)} \hfill 2023

\begin{itemize}
  \item Delivered a containerised inventory platform with JWT auth and GitHub Actions CI/CD.
\end{itemize}

\textbf{Proxmox Homelab Server} \hfill 2023

\begin{itemize}
  \item Built a private cluster with multiple VMs, Docker containers and central LDAP authentication.
\end{itemize}

\par\vspace{0.4em} 
\section*{Technical Skills}

\textbf{Programming Languages:} ROS, Rust, C, C++, Bash, Regex, Python (Django, Pandas, Numpy, Scikit-Learn), JavaScript (VueJS, ReactJS), PHP, Java

\textbf{Tools:} Git, Kubernetes, Vagrant, Docker, CI/CD (Gitlab/Github Actions/Jenkins), Terraform, Proxmox, Linux

\par\vspace{0.4em} 
\section*{Leadership \& Community Involvement}

\textbf{Elected Student Representative, Council of Studies and University Life} — UTC \hfill 2023 – 2025

\textbf{Technical Light \& Sound Association (Student Events)} — UTC \hfill 2021 – 2023

\textbf{International Experience: Lived in Africa for 8 years} \hfill 2003 – 2011
\begin{itemize}
  \item Developed strong adaptability and cross-cultural communication skills.
\end{itemize}


\par\vspace{0.4em} 
\section*{Languages}
French, English — Fluent
\end{document}